\documentclass[11pt, a4paper]{article}

% --- UNIVERSAL PREAMBLE BLOCK ---
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{fontspec}

\usepackage[english, bidi=basic, provide=*]{babel}

\babelprovide[import, onchar=ids fonts]{english}

% Set default/Latin font to Sans Serif in the main (rm) slot
\babelfont{rm}{Noto Sans}

% Add because main language is not English (Standardizing for Indian English Context)
\usepackage{enumitem}
\setlist[itemize]{label=-}

\usepackage{booktabs}
\usepackage{titlesec}
\usepackage{fancyhdr}

% Formatting Titles
\titleformat{\section}{\large\bfseries\centering\uppercase}{}{0em}{}
\titleformat{\subsection}{\bfseries\centering}{}{0em}{}
\titleformat{\subsubsection}{\bfseries}{}{0em}{}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{Page \thepage}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

\begin{center}
    \vspace*{1cm}
    {\Large \textbf{THE COMPANIES ACT, 2013}} \\
    \vspace{0.5cm}
    {\large \textbf{(COMPANY LIMITED BY SHARES)}} \\
    \vspace{1cm}
    {\Large \textbf{MEMORANDUM OF ASSOCIATION}} \\
    \vspace{0.5cm}
    {\large \textbf{OF}} \\
    \vspace{0.5cm}
    {\Large \textbf{IAH CREATIONS (OPC) PRIVATE LIMITED}}
    \vspace{2cm}
\end{center}

\noindent \textbf{I. The Name of the Company is:} IAH CREATIONS (OPC) PRIVATE LIMITED \\

\noindent \textbf{II. The Registered Office of the Company will be situated in the State of:} NCT of Delhi \\
\textit{(Note: State can be updated upon actual filing)} \\

\noindent \textbf{III. The objects for which the Company is established are:} \\

\noindent \textbf{(A) THE MAIN OBJECTS TO BE PURSUED BY THE COMPANY ON ITS INCORPORATION ARE:}

\begin{enumerate}[label=\arabic*., leftmargin=*]
    \item \textbf{Software Development \& Digital Solutions:} To carry on the business of designing, developing, testing, deploying, and maintaining commercial-grade software solutions, including rapid digital prototyping, full-scale software development, and minimum viable products (MVPs) for global markets.

    \item \textbf{Website Design \& Development:} To engage in the business of creating professional digital presence solutions, including Single Page Websites (SPW) for portfolios and resumes, and Dynamic Multi-Page Websites for corporate businesses, e-commerce platforms, and agencies, utilizing Content Management Systems (CMS) and payment gateway integrations.

    \item \textbf{Web Application Services:} To develop, maintain, and host browser-based software and Single Page Applications (SPA) using modern frameworks (React, Angular, Vue, etc.) for utilities such as calculators, dashboards, and to-do lists; and to create Multi-Tasking Dynamic Applications for enterprise needs, including SaaS products, Customer Relationship Management (CRM) systems, HR portals, and Enterprise Resource Planning (ERP) solutions.

    \item \textbf{Mobile Application Development:} To design, develop, publish, and maintain Native and Hybrid mobile applications for Android and iOS platforms, ranging from lightweight utility apps and web-view wrappers to full-featured dynamic applications involving user authentication, real-time databases, GPS integration, and AI-powered features.

    \item \textbf{Hosting, Automation \& Infrastructure:} To provide comprehensive hosting solutions, cloud integration, premium CDN services, and business workflow automation, acting on the company motto "Innovate, Automate, Host," and to facilitate server management, domain services, and third-party API integrations.

    \item \textbf{Advanced Technology Integration:} To research, develop, and integrate advanced technologies such as Artificial Intelligence (AI), microservices architecture, and real-time data analytics into business software to ensure scalability and future-readiness for clients.
\end{enumerate}

\noindent \textbf{(B) MATTERS WHICH ARE NECESSARY FOR FURTHERANCE OF THE OBJECTS SPECIFIED IN CLAUSE III(A) ARE:}

\begin{enumerate}[label=\arabic*., leftmargin=*]
    \item To acquire, purchase, or take on lease any property, rights, or privileges necessary for the business, including servers, IT infrastructure, hardware, and intellectual property rights.
    \item To enter into partnerships, joint ventures, or arrangements for sharing profits with any person or company carrying on or engaged in any business transaction which this Company is authorized to carry on.
    \item To appoint consultants, engineers, developers, designers, and technical experts for the effective management and operation of the Company’s digital services.
    \item To obtain licenses, trademarks, copyrights, and patents related to software products and brands developed by the Company.
    \item To open and operate bank accounts in the name of the Company and to draw, make, accept, endorse, discount, execute, and issue promissory notes, bills of exchange, and other negotiable or transferable instruments.
\end{enumerate}

\noindent \textbf{IV. The Liability of the member(s) is Limited:} \\
The liability of the member is limited to the amount unpaid, if any, on the shares held by him. \\

\noindent \textbf{V. The Share Capital of the Company is:} \\
The Authorized Share Capital of the Company is \textbf{Rs. 1,00,000/- (Rupees One Lakh only)} divided into \textbf{10,000 (Ten Thousand)} Equity Shares of \textbf{Rs. 10/- (Rupees Ten only)} each. \\

\noindent \textbf{VI. Nomination Clause:} \\
I, \textbf{Harshul Aggarwal}, whose name and address is given below, am the subscriber to this Memorandum of Association and I hereby nominate \textbf{[Name of Nominee]}, son/daughter of [Nominee Father's Name], resident of [Address], who shall become the member of the company in the event of my death or incapacity to contract. \\

\newpage

\begin{center}
    {\large \textbf{SUBSCRIBER TO THE MEMORANDUM}}
\end{center}

\vspace{0.5cm}

\noindent We, the several persons whose names and addresses are subscribed below, are desirous of being formed into a Company in pursuance of this Memorandum of Association, and we respectively agree to take the number of shares in the capital of the Company set opposite our respective names:

\vspace{1cm}

\begin{table}[h]
    \centering
    \renewcommand{\arraystretch}{2}
    \begin{tabular}{|p{1cm}|p{5cm}|p{3cm}|p{3cm}|p{4cm}|}
        \hline
        \textbf{S. No.} & \textbf{Name, Address, Description \& Occupation of Subscriber} & \textbf{No. of Equity Shares taken} & \textbf{Signature} & \textbf{Name, Address \& Signature of Witness} \\
        \hline
        1. & \textbf{HARSHUL AGGARWAL} \newline S/o Mr Pankaj Agagrwal \newline R/o 49/a, Sarswati Colony, Jagadhri \newline Occupation: Business & 10,000 \newline (Ten Thousand) & &  \\
         & & & & Signed before me: \newline \newline Harshul Aggarwal \newline 49/a, Sarswati Colony, Jagadhri \newline Business \\
        \hline
        \textbf{Total} & & \textbf{10,000} & & \\
        \hline
    \end{tabular}
\end{table}

\vspace{2cm}

\noindent \textbf{Place:} Yamuna Nagar \\
\noindent \textbf{Date:} [Date]

\end{document}